---
title: "An illustrative PharmaStatsR analysis workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An illustrative PharmaStatsR analysis workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette follows a two-group comparison from data inspection to a small
results table. The package data are illustrative, not clinical records. The
analysis does not establish a treatment effect or support a clinical decision.

```{r setup, include=FALSE}
library(PharmaStatsR)
```

## Inspect the analysis data

`pharma_sample` has ten observations in each treatment group. Inspect its
structure, missingness, and design before specifying a test:

```{r inspect-data}
str(pharma_sample)
table(pharma_sample$treatment, pharma_sample$dose)
anyNA(pharma_sample[c("response", "treatment")])
```

Treatment A always has dose 1 and treatment B always has dose 2. Dose and
treatment are perfectly confounded in this fixture, so their separate effects
cannot be estimated from it. The `response` and `treatment` columns have no
missing values; with other data, decide how to handle missing model variables
before fitting a model. The formula interface below rejects incomplete rows.

## Compare the groups

For this illustration, the contrast is the mean response in A minus the mean
response in B. `pharma_t_test()` returns the full `stats::t.test()` result and
uses Welch's two-sample test by default.

```{r group-comparison}
test <- pharma_t_test(response ~ treatment, data = pharma_sample)
test$estimate
test$conf.int
test$p.value
```

The confidence interval describes the group mean difference under the test's
assumptions. Neither the p-value nor the interval separates treatment from
dose in these data. For the full input and return contract, open
`help("pharma_t_test", package = "PharmaStatsR")` in R.

## Screen a fitted model

An ordinary linear model provides a separate example for residual screening.
`pharma_model_diagnostics()` reports standardized residuals, Cook's distances,
leverage, and threshold flags for this fit:

```{r model-diagnostics}
fit <- stats::lm(response ~ treatment, data = pharma_sample)
diagnostics <- pharma_model_diagnostics(fit)
head(diagnostics)
sum(diagnostics$flag, na.rm = TRUE)
```

The flags are descriptive screening heuristics, not rules for deleting rows.
These diagnostics describe the linear model; they do not validate the Welch
test above or remove the treatment–dose confounding.

## Assemble a results table

Report the direction of the contrast and its uncertainty alongside the
p-value. The formula method orders groups by their factor levels; for this
fixture that is A followed by B.

```{r results-table}
results <- data.frame(
  contrast = "A - B",
  difference = unname(test$estimate[[1L]] - test$estimate[[2L]]),
  lower_95 = unname(test$conf.int[[1L]]),
  upper_95 = unname(test$conf.int[[2L]]),
  p_value = test$p.value
)
knitr::kable(results, digits = 3)
```

For a real analysis, define the estimand, missing-data rules, assumptions,
and reporting plan before examining results. The [method inventory](https://diogoribeiro7.github.io/PharmaStatsR/method-inventory/)
distinguishes numerical reference checks from smoke tests and links the R help
for each export. The [limitations guide](https://diogoribeiro7.github.io/PharmaStatsR/limitations/)
records the package's current scope. Optional backends are covered in their
individual method guides; none is required to run this vignette.
