---
title: "Pharmaceutical Workflow Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Pharmaceutical Workflow Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette illustrates a typical workflow in pharmaceutical data analysis using functions from **PharmaStatsR**.

> **Note:** The examples in this vignette use simulated data and are intended
> for educational purposes only. They should not be relied on for
> clinical decision making.

```{r setup, include=FALSE}
library(PharmaStatsR)
```

## Data Cleaning

Use the provided datasets to demonstrate cleaning steps.

## Statistical Analysis

Examples of t-tests, ANOVA, and logistic regression.

```{r lm-example}
fit <- lm(response ~ treatment + dose, data = pharma_sample)
```

### Diagnostics

```{r diag-example}
pharma_model_diagnostics(fit)
```

### Parallel bootstrap

```{r boot-example, eval=FALSE}
stat <- function(d) mean(d$response)
pharma_parallel_bootstrap(pharma_sample, stat, R = 100)
```

```{r bayes-example, eval=FALSE}
fit <- pharma_bayesian_glm(outcome ~ dose, data = pharma_sample, iter = 500, chains = 2)
pharma_posterior_summary(fit)
```

## Reporting

Summarize results and generate basic plots.
